Cell Decompositions for Rank Two Quiver Grassmannians

### 2019-06-05 Grassmannian_cells.tex
Section 3 edits and reorganization

The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) exceptional representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors 
  \[\udim P_m=(u_m,u_{m-1}),\qquad\qquad \udim I_m=(u_{m-1},u_m).\]
  These satisfy 
  \[\Hom(P_m,P_r)=0, \qquad \Hom(I_r,I_m)=0, \qquad \Ext(P_r,P_m)=0, \qquad \Ext(I_m,I_r)=0\]
  for $1\leq r\leq m$.
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}

The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
The following homological organization is well-known.
\begin{lemma}
  \label{le:preprojective subs}
  If $\Hom(X,P_m)\ne0$ (resp. $\Ext(P_m,X)\ne0$) for some indecomposable representation $X$ and some $m\ge1$, then $X$ must be preprojective of the form $P_r$ with $1\le r\le m$ (resp. $1\le r\le m-2$).
\end{lemma}
\begin{remark}
  \label{rem:reflection recursion}
  We may identify the quiver $K(n)$ with $K(n)^{op}$ by interchanging the vertex labels.
  This induces an isomorphism of categories $\rep K(n)\cong\rep K(n)^{op}$ which we write as $M\mapsto M^\sigma$.
  Note that $\Sigma_1(M^\sigma)=(\Sigma_2 M)^\sigma$ and $\Sigma_2(M^\sigma)=(\Sigma_1 M)^\sigma$.
  Using this, we have the following:
  \begin{enumerate}
    \item The preprojective and preinjective representations satisfy the following recursions using the reflection functors:
      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m^\sigma=\Sigma_1 I_{m-1}\]
      for $m\ge2$.
      In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$.
    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then the sequences $\ses{(\Sigma_1\Sigma_2)^k M}{(\Sigma_1\Sigma_2)^k B}{(\Sigma_1\Sigma_2)^k N}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^k M}{\Sigma_2(\Sigma_1\Sigma_2)^k B}{\Sigma_2(\Sigma_1\Sigma_2)^k N}$ are exact for any $k\ge0$ and none of these representations contain preinjective direct summands.
  \end{enumerate}
\end{remark}

@@

Write $W_n:=W_{K(n)}$ for the free group generated by the arrows $\alpha_i$, $1\le i\le n$, of $K(n)$ and denote by $e\in W_n$ its identity element.
In this section, we fix compatible bases for each $\cH_m:=\Hom(P_m,P_{m+1})$ and use these to lift the (truncated) preprojective representations of the quiver $K(n)$ to the universal cover~$\widetilde{K(n)}$.
This lifting will rigidify the situation, allowing more precise control over these representations and their subrepresentation structure.
Of particular importance is Corollary~\ref{cor:perpendicular} which has no reasonable analogue for $K(n)$.
One main advantage of the lifting is that those truncated preprojectives which can be lifted are exceptional representations on the universal covering quiver $\widetilde{K(n)}$.

@@

To construct the lifts, first recall that applying the BGP-reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying the iterated reflection $\tilde\Sigma_i:=\prod_{w\in W_n}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
Moreover, under this operation all sinks of~$\widetilde{K(n)}$ become sources and vice versa.
The preprojective lifts we use are defined by the following analogue of the recursions of Remark~\ref{rem:reflection recursion}.
\begin{itemize}
  \item We consider the lift $\tilde P_1$ satisfying $\udim(\tilde P_1)_{(1,e)}=1$ and $\udim(\tilde P_1)_{(i,w)}=0$ for $(i,w)\neq (1,e)$.
  \item We consider the lift $\tilde P_2$ satisfying $\udim(\tilde P_2)_{(2,e)}=\udim(\tilde P_2)_{(1,\alpha_i)}=1$ for $1\le i\le n$ and $\udim(\tilde P_2)_{(i,w)}=0$ for $(i,w)\notin\{(2,e),(1,\alpha_1),\ldots,(1,\alpha_n)\}$.
  \item For $m\geq 3$, we build the lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translates.
    More precisely, we set
    \begin{align}
      \label{eq:recursive covers}
      \tilde P_m:=\tilde\Sigma_2(\tilde P_{m-1})^{\sigma}\qquad\text{or}\qquad\tilde P_{m+1}:=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1},
    \end{align}
    where $(-)^\sigma:\rep\widetilde{K(n)}^{op}\to\rep\widetilde{K(n)}$ is the lift of the corresponding functor for $K(n)$.
\end{itemize}

It will be rather important that our chosen lifts of $P_{2\ell}$ for $\ell\ge1$ and our chosen lifts of $P_{2\ell-1}$ for $\ell\ge1$ live on two different components of the universal covering quiver.
Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via translation, i.e.~$w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
Following the notation of Section~\ref{sec:covering}, we write $\tilde P_{m,w}$ for the representation of $\widetilde{K(n)}$ obtained by translating the lifted preprojective representation~$\tilde P_m$ by the action of $w\in W_n$.
To simplify the notation, we abbreviate $\tilde P_{2\ell-1,j}:=\tilde P_{2\ell-1,\alpha_j}$ and $\tilde P_{2\ell,j}:=\tilde P_{2\ell,\alpha_j^{-1}}$.
\begin{lemma}
  \label{le:shifted subreps}
  For each $m\ge1$, the representation $\tilde P_{m+1}$ has precisely $n$ subrepresentations covering $P_m$.
  These are the representations $\tilde P_{m,j}$ corresponding to the $n$ different arrows of $K(n)$. 
\end{lemma}
\begin{proof}
  This is clear for $m=1$ and follows in general by applying the recursion \eqref{eq:recursive covers}.
\qed\end{proof}
\begin{remark}
  Note that the dimension vectors of the lifted preprojectives $\tilde P_m$ are symmetric under permutations of the arrows of $K(n)$ (or rather the corresponding operation on $\widetilde{K(n)}$).
  In particular, they all have the same central vertex $(1,e)$ if $m$ is odd and central vertex $(2,e)$ if $m$ is even.
\end{remark}

@@

  The representation $\tilde P_2$ is defined by the following quiver:
  \begin{equation}
    \label{dia:P2 quiver}
    \xymatrix@R40pt@C10pt{&(2,e)\ar_{\alpha_1}[ld]\ar^{\alpha_n}[rd]&\\ (1,\alpha_1)&\cdots&(1,\alpha_n).}
  \end{equation}
  Then $\tilde P_{1,j}\subset\tilde P_2$ corresponds to the one-dimensional space at vertex $(1,\alpha_j)$.
  Write $\cA_i$ for the quiver obtained from the one above by erasing the arrow $\alpha_i$ and the corresponding sink.

@@

The next result establishes some basic homological properties of these translated preprojective representations.
\begin{lemma}
  \label{le:homdecomposition}
  For $m\geq 1$, the following hold.
  \begin{enumerate}
    \item We have $\Hom(P_m,P_{m+1})\cong\bigoplus\limits_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m+1})$, where each $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ is one-dimensional.
    \item The representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e.\ for $i\neq j$ we have 
      \[\Hom(\tilde P_{m,i},\tilde P_{m,j})=0=\Ext(\tilde P_{m,i},\tilde P_{m,j}).\]
    \item For $j\in\{1,\ldots,n\}$, we have
      \[\Hom(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m,j},\tilde P_{m+1})=0.\]
    \item For each proper subset $I\subsetneq\{1,\ldots,n\}$, there exists a truncated preprojective representation~$\tilde P_{m+1}^I$ fitting into an exact sequence 
      \begin{equation}
        \label{ses1}
        \xymatrix{ 0 \ar[r] & \bigoplus_{i\in I} \tilde P_{m,i} \ar[r]^{ev_I} & \tilde P_{m+1} \ar[r]^{\pi_{m+1}^I} & \tilde P_{m+1}^I \ar[r] & 0}.
      \end{equation}
      Moreover, $G(\tilde P_{m+1}^I)$ is a truncated preprojective of $K(n)$ for each $I\subsetneq\{1,\ldots,n\}$.
  \end{enumerate}
\end{lemma}
\begin{remark}
  Note that when $I=\varnothing$, it follows from the definition that $\tilde P_{m+1}^I=\tilde P_{m+1}$.
\end{remark}
\begin{proof}
  Part (1) is immediate from Theorem~\ref{covering}.
  Part (2) is also a consequence of Theorem~\ref{covering}.
  Indeed, for $1\leq j\leq n$, we have 
  $$\CC\cong\Hom(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m,j}).$$
  But $\Hom(\tilde P_{m,j},\tilde P_{m,j})\cong\CC$ and so we must have $\Hom(\tilde P_{m,i},\tilde P_{m,j})=0$ for $i\neq j$.
  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,j})$ follows in the same manner using that $P_m$ is exceptional.

@@

  For part (4), observe that under the isomorphism from part (1) the subset $I\subsetneq\{1,\ldots,n\}$ corresponds to the subspace $V\subset \cH_m$ spanned by the generators of the direct summands $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ for $i\in I$.
  The map $\bigoplus_{i\in I} \tilde P_{m,i}\to\tilde P_{m+1}$ is then a lift of the evaluation morphism $ev_V:P_m\otimes V\to P_{m+1}$ and hence is injective by Lemma~\ref{le:injective evaluation maps}.
  Taking the cokernel defines the truncated preprojective $\tilde P_{m+1}^I$ and the preceding discussion shows that $G(\tilde P_{m+1}^I)\cong P_{m+1}^V$ is truncated preprojective as well.
\qed\end{proof}

@@

In what follows, we will need to carefully understand the homological properties of the truncated preprojectives for $\widetilde{K(n)}$.
\begin{lemma}
  \label{le:properties}
  For $m\geq1$ and $I\subsetneq\{1,\ldots,n\}$, the following hold.
  \begin{enumerate}
    \item For $j\in\{1,\ldots,n\}$, we have $\Ext(\tilde P_{m,j},\tilde P_{m+1}^I)=0$.  Also, $\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\ne0$ if and only if $j\not\in I$, in which case 
      \[\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Hom(\tilde P_{m,j},\tilde P_{m+1})\cong\CC.\]
    \item We have $\Hom(\tilde P_{m+1},\tilde P_{m+1}^I)\cong\CC$ and $\Ext(\tilde P_{m+1},\tilde P_{m+1}^I)=0$. 
    \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$.
      Also, $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ne0$ if and only if $j\in I$, in which case  
      \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\] 
      is generated by the non-split sequence
      \[\xymatrix{0 \ar[r] & \tilde P_{m,j} \ar[r] & \tilde P_{m+1}^{I\setminus\{j\}} \ar[r] & \tilde P_{m+1}^I \ar[r] & 0}.\]
    \item For any $J\subsetneq\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^J,\tilde P_{m+1}^I)\ne0$ if and only if $J\subset I$, in which case
      \[\Hom(\tilde P_{m+1}^J,\tilde P_{m+1}^I)\cong\CC\quad\text{and}\quad\Ext(\tilde P_{m+1}^J,\tilde P_{m+1}^I)=0.\]
      In particular, $\tilde P_{m+1}^I$ is an exceptional representation of $\widetilde{K(n)}$.
  \end{enumerate}
\end{lemma} 
\begin{proof}
  Applying $\Hom(\tilde P_{m,j},-)$ to the sequence \eqref{ses1} gives the exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(\tilde P_{m,j},\bigoplus_{i\in I} \tilde P_{m,i}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}^I) \ar[r] & 0},\]
  where the final zero follows from Lemma~\ref{le:homdecomposition}.(2).
  This also gives an isomorphism $\Ext(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Ext(\tilde P_{m,j},\tilde P_{m+1})=0$ by Lemma~\ref{le:homdecomposition}.(3).
  Now the middle space in the sequence above is one-dimensional while the left-hand space vanishes if and only if $j\notin I$, this proves part (1).

  Part (2) is an immediate consequence of Lemma~\ref{le:unique preprojective morphism} together with Theorem~\ref{covering} or can be obtained directly by applying $\Hom(\tilde P_{m+1},-)$ to the sequence \eqref{ses1}.
  The first part of (3) follows from Theorem~\ref{covering} together with Lemma~\ref{le:basic homological properties}.
  For the second part of (3), we apply $\Hom(-,\tilde P_{m,j})$ to the sequence \eqref{ses1}.
  Then taking into account Lemma~\ref{le:homdecomposition} part (3), we get the isomorphism
  \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Hom(\textstyle{\bigoplus_{i\in I}}\tilde P_{m,i},\tilde P_{m,j}).\] 
  Then Lemma~\ref{le:homdecomposition}.(2) gives the final claim of part (3).

  Part (4) follows by applying $\Hom(-,\tilde P^I_{m+1})$ to the sequence \eqref{ses1} for $J$ then using parts (1) and (2).
\qed\end{proof}

\begin{example}
  \label{ex:truncated lifts}
  Fix $I\subsetneq\{1,\ldots,n\}$.
  Building on Example~\ref{ex:lifted preprojectives}, we describe here the truncated preprojectives $\tilde P_m^I$ for $m=2,3,4$.
  Following Lemma~\ref{le:properties}.(4), we can do this by simply specifying their dimension vectors as we did above.

@@

We now introduce notation for locating specific lifted preprojectives as subrepresentations of our standard lifted preprojective representations.
Since we work only on two fixed components of $\widetilde{K(n)}$, the following notation will be useful in describing paths in these components.
For $k\ge1$, set
\[A_1^{(k)}:=\{(i_1,\ldots,i_k)\mid i_j\in\{1,\ldots,n\}\text{ for $1\le j\le k$}\}.\]
Depending on context (in particular, the parity of $m$), we will either identify the word~$(i_1,\ldots,i_k)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_k}^{(-1)^{k+1}}\in W_n$ when $m$ is even or with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_k}^{(-1)^k}\in W_n$ when $m$ is odd.

>>>>

The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) exceptional representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors 
  \[\udim P_m=(u_m,u_{m-1}),\qquad\qquad \udim Q_m=(u_{m-1},u_m).\]
  These satisfy 
  \[\Hom(P_m,P_r)=0, \qquad \Hom(Q_r,Q_m)=0, \qquad \Ext(P_r,P_m)=0, \qquad \Ext(Q_m,Q_r)=0\]
  for $1\leq r\leq m$.
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $Q_m^{a_1}\oplus Q_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}

The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $Q_m$ are called \emph{preinjective}.
The following homological organization is well-known.
\begin{lemma}
  \label{le:preprojective subs}
  If $\Hom(X,P_m)\ne0$ (resp. $\Ext(P_m,X)\ne0$) for some indecomposable representation $X$ and some $m\ge1$, then $X$ must be preprojective of the form $P_r$ with $1\le r\le m$ (resp. $1\le r\le m-2$).
\end{lemma}
\begin{remark}
  \label{rem:reflection recursion}
  We may identify the quiver $K(n)$ with $K(n)^{op}$ by interchanging the vertex labels.
  This induces an isomorphism of categories $\rep K(n)\cong\rep K(n)^{op}$ which we write as $M\mapsto M^\sigma$.
  Note that $\Sigma_1(M^\sigma)=(\Sigma_2 M)^\sigma$ and $\Sigma_2(M^\sigma)=(\Sigma_1 M)^\sigma$.
  Using this, we have the following:
  \begin{enumerate}
    \item The preprojective and preinjective representations satisfy the following recursions using the reflection functors:
      \[P_1=S_1,\quad P_m^\sigma=\Sigma_2 P_{m-1},\quad Q_1=S_2,\quad Q_m^\sigma=\Sigma_1 I_{m-1}\]
      for $m\ge2$.
      In particular, we have $P_{m-1}=\tau P_{m+1}$ and $Q_{m+1}=\tau Q_{m-1}$ for $m\ge2$.
    \item If $\ses{M}{B}{N}$ is a short exact sequence such that no direct summand of $M$, $B$, nor $N$ is preinjective, then the sequences $\ses{(\Sigma_1\Sigma_2)^k M}{(\Sigma_1\Sigma_2)^k B}{(\Sigma_1\Sigma_2)^k N}$ and $\ses{\Sigma_2(\Sigma_1\Sigma_2)^k M}{\Sigma_2(\Sigma_1\Sigma_2)^k B}{\Sigma_2(\Sigma_1\Sigma_2)^k N}$ are exact for any $k\ge0$ and none of these representations contain preinjective direct summands.
  \end{enumerate}
\end{remark}

@@

Write $W_n:=W_{K(n)}$ for the free group generated by the arrows $\alpha_i$, $1\le i\le n$, of $K(n)$ and denote by $e\in W_n$ its identity element.
In this section, we fix compatible bases for each $\cH_m:=\Hom(P_m,P_{m+1})$ and use these to lift the (truncated) preprojective representations of the quiver $K(n)$ to the universal cover~$\widetilde{K(n)}$.
This lifting will rigidify the situation, allowing more precise control over these representations and their subrepresentation structure.
Of particular importance is Corollary~\ref{cor:perpendicular} which has no reasonable analogue for $K(n)$.
Another main advantage of the lifting is that those truncated preprojectives which can be lifted are exceptional representations on the universal covering quiver $\widetilde{K(n)}$.

@@

To construct the lifts, first recall that applying the BGP-reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying the iterated reflection $\tilde\Sigma_i:=\prod_{w\in W_n}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
Moreover, under this operation all sinks of~$\widetilde{K(n)}$ become sources and vice versa.
The preprojective lifts we use are defined by the following analogue of the recursion of Remark~\ref{rem:reflection recursion}.
\begin{itemize}
  \item We consider the lift $\tilde P_1$ satisfying $\udim(\tilde P_1)_{(1,e)}=1$ and $\udim(\tilde P_1)_{(i,w)}=0$ for $(i,w)\neq (1,e)$.
  \item We consider the lift $\tilde P_2$ satisfying $\udim(\tilde P_2)_{(2,e)}=\udim(\tilde P_2)_{(1,\alpha_i)}=1$ for $1\le i\le n$ and $\udim(\tilde P_2)_{(i,w)}=0$ for $(i,w)\notin\{(2,e),(1,\alpha_1),\ldots,(1,\alpha_n)\}$.
  \item For $m\geq 3$, we build the lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translates.
    More precisely, we set
    \begin{align}
      \label{eq:recursive covers}
      \tilde P_m:=\tilde\Sigma_2(\tilde P_{m-1})^{\sigma}\qquad\text{or}\qquad\tilde P_{m+1}:=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1},
    \end{align}
    where $(-)^\sigma:\rep\widetilde{K(n)}^{op}\to\rep\widetilde{K(n)}$ is the lift of the corresponding functor for $K(n)$.
\end{itemize}

It will be rather important that our chosen lifts of $P_{2\ell}$ for $\ell\ge1$ and our chosen lifts of $P_{2\ell-1}$ for $\ell\ge1$ live on two different components of the universal covering quiver.
Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via left translation, i.e.~$w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
Following the notation of Section~\ref{sec:covering}, we write $\tilde P_{m,w}$ for the representation of $\widetilde{K(n)}$ obtained by translating the lifted preprojective representation~$\tilde P_m$ by the action of $w\in W_n$.
\begin{remark}
  \label{rem:abbreviations}
  To simplify the notation, we abbreviate $\tilde P_{2\ell-1,i}:=\tilde P_{2\ell-1,\alpha_i}$ and $\tilde P_{2\ell,i}:=\tilde P_{2\ell,\alpha_i^{-1}}$ for $\ell\ge1$ and $i\in\{1,\ldots,n\}$.
\end{remark}
\begin{lemma}
  \label{le:shifted subreps}
  For each $m\ge1$, the representation $\tilde P_{m+1}$ has precisely $n$ subrepresentations covering $P_m$.
  These are the representations $\tilde P_{m,j}$ corresponding to the $n$ different arrows of $K(n)$. 
\end{lemma}
\begin{proof}
  This is clear for $m=1$ and follows in general by applying the recursion \eqref{eq:recursive covers}.
\qed\end{proof}
\begin{remark}
  Note that the dimension vectors of the lifted preprojectives $\tilde P_m$ are symmetric under permutations of the arrows of $K(n)$ (or rather the corresponding operation on $\widetilde{K(n)}$).
  In particular, they all have the same central vertex $(1,e)$ if $m$ is odd and central vertex $(2,e)$ if $m$ is even.
\end{remark}

@@

  The representation $\tilde P_2$ is defined by the following quiver:
  \begin{equation}
    \label{dia:P2 quiver}
    \xymatrix@R40pt@C10pt{&(2,e)\ar_{\alpha_1}[ld]\ar^{\alpha_n}[rd]&\\ (1,\alpha_1)&\cdots&(1,\alpha_n).}
  \end{equation}
  Then $\tilde P_{1,j}\subset\tilde P_2$ corresponds to the one-dimensional space at vertex $(1,\alpha_j)$.
  Write $\cA_i$ for the quiver obtained from the one above by erasing the arrow $\alpha_i$ and the corresponding sink $(1,\alpha_i)$.

@@

The next result establishes some basic homological properties of these translates of preprojective representations.
\begin{lemma}
  \label{le:homdecomposition}
  For $m\geq 1$, the following hold.
  \begin{enumerate}
    \item We have $\Hom(P_m,P_{m+1})\cong\bigoplus\limits_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m+1})$, where each $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ is one-dimensional.
    \item The representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e.\ for $i\neq j$ we have 
      \[\Hom(\tilde P_{m,i},\tilde P_{m,j})=0=\Ext(\tilde P_{m,i},\tilde P_{m,j}).\]
    \item For $j\in\{1,\ldots,n\}$, we have
      \[\Hom(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m,j},\tilde P_{m+1})=0.\]
    \item For each proper subset $I\subsetneq\{1,\ldots,n\}$, there exists a truncated preprojective representation~$\tilde P_{m+1}^I$ fitting into an exact sequence 
      \begin{equation}
        \label{ses1}
        \xymatrix{ 0 \ar[r] & \bigoplus_{i\in I} \tilde P_{m,i} \ar[r]^{ev_I} & \tilde P_{m+1} \ar[r]^{\pi_{m+1}^I} & \tilde P_{m+1}^I \ar[r] & 0}.
      \end{equation}
      Moreover, $G(\tilde P_{m+1}^I)$ is a truncated preprojective of $K(n)$ for each $I\subsetneq\{1,\ldots,n\}$.
  \end{enumerate}
\end{lemma}
\begin{remark}
  Note that when $I=\varnothing$, it follows from the definition that $\tilde P_{m+1}^I=\tilde P_{m+1}$.
\end{remark}
\begin{proof}
  Part (1) is immediate from Theorem~\ref{covering}.
  Part (2) is also a consequence of Theorem~\ref{covering}.
  Indeed, for $1\leq j\leq n$, we have 
  $$\CC\cong\Hom(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m,j}).$$
  But $\Hom(\tilde P_{m,j},\tilde P_{m,j})\cong\CC$ and so we must have $\Hom(\tilde P_{m,i},\tilde P_{m,j})=0$ for $i\neq j$.
  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,j})$ follows in the same manner using that $P_m$ is exceptional.

@@

  For part (4), observe that under the isomorphism from part (1) the subset $I\subsetneq\{1,\ldots,n\}$ corresponds to the subspace $V\subset \cH_m$ spanned by generators of the direct summands $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ for $i\in I$.
  The map $\bigoplus_{i\in I} \tilde P_{m,i}\to\tilde P_{m+1}$ is then a lift of the evaluation morphism $ev_V:P_m\otimes V\to P_{m+1}$ and hence is injective by Lemma~\ref{le:injective evaluation maps}.
  Taking the cokernel defines the truncated preprojective $\tilde P_{m+1}^I$ and the preceding discussion shows that $G(\tilde P_{m+1}^I)\cong P_{m+1}^V$ is truncated preprojective as well.
\qed\end{proof}

@@

In what follows, we will need to carefully understand the homological properties of the truncated preprojectives for $\widetilde{K(n)}$.
\begin{lemma}
  \label{le:properties}
  For $m\geq1$ and $I\subsetneq\{1,\ldots,n\}$, the following hold.
  \begin{enumerate}
    \item For $j\in\{1,\ldots,n\}$, we have $\Ext(\tilde P_{m,j},\tilde P_{m+1}^I)=0$.  Also, $\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\ne0$ if and only if $j\not\in I$, in which case 
      \[\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Hom(\tilde P_{m,j},\tilde P_{m+1})\cong\CC.\]
    \item We have $\Hom(\tilde P_{m+1},\tilde P_{m+1}^I)\cong\CC$ and $\Ext(\tilde P_{m+1},\tilde P_{m+1}^I)=0$. 
    \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$.
      Also, $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ne0$ if and only if $j\in I$, in which case  
      \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\] 
      is generated by the non-split sequence
      \[\xymatrix{0 \ar[r] & \tilde P_{m,j} \ar[r] & \tilde P_{m+1}^{I\setminus\{j\}} \ar[r] & \tilde P_{m+1}^I \ar[r] & 0}.\]
    \item For any $J\subsetneq\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^J,\tilde P_{m+1}^I)\ne0$ if and only if $J\subseteq I$, in which case
      \[\Hom(\tilde P_{m+1}^J,\tilde P_{m+1}^I)\cong\CC\quad\text{and}\quad\Ext(\tilde P_{m+1}^J,\tilde P_{m+1}^I)=0.\]
      In particular, $\tilde P_{m+1}^I$ is an exceptional representation of $\widetilde{K(n)}$.
    \item For each proper subset $J\subsetneq I$, there is an exact sequence 
      \begin{equation*}
        \xymatrix{ 0 \ar[r] & \bigoplus_{i\in I\setminus J} \tilde P_{m,i} \ar[r] & \tilde P^J_{m+1} \ar[r]^{\tilde\pi_{m+1}^{J,I}} & \tilde P_{m+1}^I \ar[r] & 0}.
      \end{equation*}
      For any sequence of proper subsets $K\subsetneq J\subsetneq I$, the quotient maps satisfy $\pi_{m+1}^{K,I}=\pi_{m+1}^{J,I}\circ\pi_{m+1}^{K,J}$ and $\pi_{m+1}^I=\pi_{m+1}^{J,I}\circ\pi_{m+1}^J$.
  \end{enumerate}
\end{lemma} 
\begin{proof}
  Applying $\Hom(\tilde P_{m,j},-)$ to the sequence \eqref{ses1} gives the exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(\tilde P_{m,j},\bigoplus_{i\in I} \tilde P_{m,i}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}^I) \ar[r] & 0},\]
  where the final zero follows from Lemma~\ref{le:homdecomposition}.2.
  This also gives an isomorphism $\Ext(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Ext(\tilde P_{m,j},\tilde P_{m+1})=0$ by Lemma~\ref{le:homdecomposition}.3.
  Now the middle space in the sequence above is one-dimensional while the left-hand space vanishes if and only if $j\notin I$, this proves part (1).

  Part (2) is an immediate consequence of Lemma~\ref{le:unique preprojective morphism} together with Theorem~\ref{covering} or can be obtained directly by applying $\Hom(\tilde P_{m+1},-)$ to the sequence \eqref{ses1}.
  The first part of (3) follows from Theorem~\ref{covering} together with Lemma~\ref{le:basic homological properties}.
  For the second part of (3), we apply $\Hom(-,\tilde P_{m,j})$ to the sequence \eqref{ses1}.
  Then taking into account Lemma~\ref{le:homdecomposition}.3, we get the isomorphism
  \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\Hom(\textstyle{\bigoplus_{i\in I}}\tilde P_{m,i},\tilde P_{m,j}),\] 
  and Lemma~\ref{le:homdecomposition}.2 gives the final claim of part (3).

  Part (4) follows by applying $\Hom(-,\tilde P^I_{m+1})$ to the sequence \eqref{ses1} for $J$ then using parts (1) and (2).

  The exactness in the first half of (5) follows from a routine chase through the following commutative diagram:
  \begin{equation*}
    \xymatrix{ 
      & 0 \ar[d] & 0 \ar[d] & 0 \ar[d] & \\
      0 \ar[r] & \bigoplus_{i\in J} \tilde P_{m,i} \ar@{=}[r] \ar[d] & \bigoplus_{i\in J} \tilde P_{m,i} \ar[r] \ar[d] & 0 \ar[r] \ar[d] & 0\\
      0 \ar[r] & \bigoplus_{i\in I} \tilde P_{m,i} \ar[r] \ar[d] & \tilde P_{m+1} \ar[r] \ar[d] & \tilde P_{m+1}^I \ar[r] \ar@{=}[d] & 0\\
      0 \ar[r] & \bigoplus_{i\in I\setminus J} \tilde P_{m,i} \ar[r] \ar[d] & \tilde P^J_{m+1} \ar[r] \ar[d] & \tilde P_{m+1}^I \ar[r] \ar[d] & 0 \\
      & 0 & 0 & 0 &
    }
  \end{equation*}
  This and a similar diagram give the equalities at the end of (5).
\qed\end{proof}

\begin{example}
  \label{ex:truncated lifts}
  Fix $I\subsetneq\{1,\ldots,n\}$.
  Building on Example~\ref{ex:lifted preprojectives}, we describe here the truncated preprojectives $\tilde P_m^I$ for $m=2,3,4$.
  Following Lemma~\ref{le:properties}.4, we can do this by simply specifying their dimension vectors as we did above.

@@

We now introduce notation for locating specific lifted preprojectives as subrepresentations of our standard lifted preprojective representations $\tilde P_{m+1}$.
To each word $\ui=(i_1,\ldots,i_k)$, with $1\leq k\leq m$, we associate a preprojective subrepresentation~$\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
More precisely, we obtain from Lemma~\ref{le:shifted subreps} a sequence of preprojective subrepresentations which uniquely determines the desired inclusion:
\[\tilde P_{m+1-k,\ui}\subset\tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset\tilde P_{m-1,(i_1,i_2)}\subset\tilde P_{m,i_1}\subset\tilde P_{m+1}.\]
\begin{remark}
  Following Remark~\ref{rem:abbreviations}, we will either identify a word~$\ui=(i_1,\ldots,i_k)$ with the element 
  \[\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_k}^{(-1)^{k+1}}\in W_n\]
  when $m$ is even or with the element 
  \[\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_k}^{(-1)^k}\in W_n\]
  when $m$ is odd.
  In this way, a subscript $\ui$ on a representation or morphism will denote the corresponding shift inside $\rep\widetilde{K(n)}$.
\end{remark}
